---
title: "Module3Test"
author: "Markus Jury"
date: "2018 M02 16"
output:
  pdf_document:
    df_print: tibble
    highlight: haddock
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#   Sample Solutions to Module 3 Exercises
###   Author:  Andrew Proctor

## Preliminaries ---------------------------------------------------------------

### Initialize packages
```{r}
library(rio)
library(tidyverse)
``` 

## Data Preparation -------------------------------------------------------------

### Import files
```{r}
characteristics <- import("./fmli161x.sas7bdat") %>% as.tibble()
expenditures <- import("./mtbi161x.sas7bdat")%>% as.tibble()
```

### Make column names lower case
```{r}
colnames(characteristics) <- colnames(characteristics) %>% map(tolower)
colnames(expenditures) <- colnames(expenditures) %>% map(tolower)
```

### Select only desired variables in each data set
```{r}
characteristics <- characteristics %>% select(newid,hh_cu_q,educ_ref,
                                                    creditx, region, fincbtxm)
expenditures <- expenditures %>% select(newid,cost,ref_mo,ref_yr)
```

### Rename selected variables
```{r}
characteristics <- characteristics %>% rename(hh_size=hh_cu_q, 
                                              hh_income=fincbtxm)
```

### Make columns except for "newid" numeric
```{r}
characteristics[,-1] <- characteristics[,-1] %>% map(as.numeric)
expenditures[,-1] <- expenditures[,-1] %>% map(as.numeric)
```

### Create 80% sample of data frames
```{r}
characteristics <- sample_frac(characteristics, 0.8)
expenditures <- sample_frac(expenditures, 0.8)
```

### Practice different joins
```{r}
cex_data <- left_join(expenditures, characteristics, by="newid")
cex_data_inner <- semi_join(expenditures, characteristics, by="newid")
cex_data_semi <- semi_join(expenditures, characteristics, by="newid")
cex_data_anti <- anti_join(expenditures, characteristics, by="newid")
```

### Create regions indicators
```{r}
cex_data <- cex_data %>% mutate(region1 = ifelse(region == 1,1,0),
                                region2 = ifelse(region == 2,1,0),
                                region3 = ifelse(region == 3,1,0),
                                region4 = ifelse(region == 4,1,0),
                                region4 = ifelse(is.na(region),1,0)
                                )
```
                                
### Define ols function
```{r}
my_ols <- function(indvars,depvar){

  
### Keep only observations with no missing values for indvars and depvar
X <- indvars[(!is.na(indvars)) & (!is.na(depvar))]
y <- depvar[(!is.na(indvars)) & (!is.na(depvar))] 
 
#### Create constant vector
ones_vec <- matrix(rep(1), length(X))
  
### Create matrix X equal to constant vec and indvars
X <- cbind(ones_vec, X)
  
### Name constant column "constant"
colnames(X)[1] <- "constant"

### Solve for coefficients
beta <- solve(t(X)%*%X) %*% (t(X)%*%y)
    colnames(beta) <- "Estimate"
  
### Convert to data frame
beta <- as.data.frame(beta)
}
```

## Analysis ---------------------------------------------------------------------

### Estimate Coefficients
```{r}
coeffs_schooling <- my_ols(cex_data$educ_ref, cex_data$cost)
```
### Display results
```{r}
coeffs_schooling
```
