---
title: "Module5Exercise"
author: "Markus Jury"
date: "February 23, 2018"
output: html_document
---
##libraries
```{r,results='hide',message=FALSE}
library(tidyverse)
library(Ecdat)
library(rio)
```

##import data (as tibbles)
```{r}
wdi_data <- import("wdi_data.rds") %>% as.tibble()
```

```{r}
affairs <- Fair %>% as.tibble()
```

##Selecting variables
```{r}
affairs %>% select("nbaffairs","ym","child","rate","age")
```

##renaming variables
```{r}
affairs <- affairs %>%
  rename(affairs = nbaffairs,
         yrsmarr = ym,
         mrating = rate)
```

##converting mrating
```{r}
affairs$mrating <- as.factor(affairs$mrating)
str(affairs)
```

##affairs regression
```{r}
affairsreg <- lm(affairs ~ age + child + yrsmarr + I(yrsmarr^2), data=affairs)
summary(affairsreg)
```

##model diagnostics
```{r,results='hide',message=FALSE}
library(lmtest)
```

```{r}
bptest(affairsreg)
resettest(affairsreg)
```
Our result from the Breusch-Pagan test is highly significant.
We therefore reject the H0 of homoscedastic errors.

Our result from the RESET test is not significant at any level.
We therefore fail to reject the H0 that our model has the correct functional
form given our chosen variables.

##Create Ye Olde Barre Plotte
```{r,results='hide',message=FALSE}
library(ggthemes)
```

```{r}
affairssum <- affairs %>% group_by(mrating) %>% 
  summarize(avgaffairs = mean(affairs))
ggplot(affairssum, aes(x=mrating, y=avgaffairs)) + geom_bar(stat="identity") + 
ggtitle("Affairs by Marital Rating") + xlab("Marital Rating") + 
ylab("Average # of Affairs") + theme_stata()
```

Moving on to wdi_data

##Scatterplots
```{r}
ggplot(wdi_data, aes(x=secondary.complet.avg, y=femaletomale.avg, col= 
                       GDP.avg)) + 
geom_point() + ggtitle("Secondary School Completion by Employment Sex Ratio") + 
xlab("Secondary School Completion Ratio") + ylab("Female-to-Male Employment") +
scale_color_gradient(low="red2",high="green", name="Average GDP")
```

```{r}
ggplot(wdi_data, aes(x=secondary.complet.avg, y=unemp.basic.educ., col= 
                       GDP.avg)) + 
geom_point() + 
ggtitle("Secondary School Completion by Unemployment 
        For Those With Basic Education") + 
xlab("Secondary School Completion Ratio") +
ylab("Unemployment For Those With Basic Education") +
scale_color_gradient(low="red2",high="green", name="Average GDP")
```

##Pooled Regression
```{r,results='hide',message=FALSE}
library(broom)
```

```{r}
schoolreg <- lm(GDP.avg ~ secondary.complet.avg, data=wdi_data)
tidy(schoolreg)
```

##Test for Autocorrelation
```{r}
bgtest(schoolreg)
```

##Fixed Effects
```{r,results='hide',message=FALSE}
library(plm)
```

```{r}
schoolregfix <- plm(GDP.avg ~ secondary.complet.avg, data=wdi_data, 
                    index=c("country", "year"), model="within", effect="twoway")
tidy(schoolregfix)
```

##Autocorrelation Robust Interference

```{r}
tidy(coeftest(schoolregfix, vcov = vcovHC(schoolregfix, type="HC1")))
```
